Figure: the scatterblob

### 2022-06-06 R/roles_table.Rmd
move data
edit "repo" to "repository" in raw data

```{r wrangle, include=FALSE}
roles <- read_csv(here("R", "collaborator_roles.csv"))

roles_wide <-
  roles %>%
  tidyr::fill(Role, Description) %>% 
  pivot_wider(names_from = `GitHub Feature`, values_from = `Use Case`) %>% 
  select(Role, `GitHub repo`, README, Issue, Discussion, `Pull Request`, Fork, `GitHub Pages`) %>% 
  mutate(across(everything(), ~replace_na(.x, "")))
```

>>>>

```{r wrangle, include=FALSE}
roles <- read_csv(here("data", "collaborator_roles.csv"))

roles_wide <-
  roles %>%
  tidyr::fill(Role, Description) %>% 
  pivot_wider(names_from = `GitHub Feature`, values_from = `Use Case`) %>% 
  select(Role, `GitHub repository`, README, Issue, Discussion, `Pull Request`, Fork, `GitHub Pages`) %>% 
  mutate(across(everything(), ~replace_na(.x, "")))
```
